\normalfont \normalsize \huge Battle of Online and Offline Consumption: \\ Comparative Analysis of Amazon and Walmart Stocks

### 2017-06-16 Battle_of_Online_and_Offline_Consumption.tex
Before Section 5

\documentclass[paper=a4, fontsize=13pt]{article} 
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{amstext}
\usepackage{subfigure}
\RequirePackage{graphicx}
\RequirePackage{longtable,multirow,hhline,tabularx,array}
\usepackage[english]{babel} 
\RequirePackage{colortbl,booktabs}
\linespread{1.5}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[scale = 0.4]{img/cf_AMZN}
\caption{ACF and PACF of Amazon Stock}
\label{cf_AMZN}
\end{figure}

\begin{figure}[!htbp]
\centering
\includegraphics[scale = 0.4]{img/cf_WMT}
\caption{ACF and PACF of Walmart Stock}
\label{cf_WMT}
\end{figure}

@@

The $a_t^2$ series is then used to check for conditional heteroscedasticity (ARCH effects). To consolidate the observation results in Figure \ref{cf_AMZN}.(c), we perform the Ljung–Box statistics Q(m) to the $\{a_t^2\}$ series. The null hypothesis is that the first m lags of ACF of the $a_t^2$ series are zero. The results of Ljung–Box test shows an ARCH effect exists in this log return series with Q(5) = 9.6519, the p-value of which is close to zero.

@@

@@

\begin{table}[!htbp] \centering 
  \caption{Results of Estimation of Two Volatility Models for AMZN Stock} 
  \label{est_AMZN} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline
 & ARCH(1) & GARCH(1,1) \\ 
\hline \\[-1.8ex] 
 mu & 0.115$^{**}$ & 0.137$^{***}$ \\ 
  & (0.046) & (0.046) \\ 
 omega & 3.515$^{***}$ & 1.020$^{***}$ \\ 
  & (0.149) & (0.344) \\ 
 alpha1 & 0.168$^{***}$ & 0.129$^{***}$ \\ 
  & (0.036) & (0.032) \\ 
 beta1 &  & 0.637$^{***}$ \\ 
  &  & (0.098) \\ 
\hline \\[-1.8ex] 
Observations & 1761 & 1761 \\ 
Log Likelihood & -3724.855 & -3720.010 \\ 
Akaike Inf. Crit. & 4.234 & 4.229 \\ 
Bayesian Inf. Crit. & 4.243 & 4.242 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

Following the same logic as in the previous section, we select ARCH(1) model for WMT Stock. Since there’s little difference between these two models based on their log likelihood, AIC, and BIC, our selection is rather subjective.

\begin{table}[!htbp] \centering 
  \caption{Ljung-Box tests for ARCH(1) and GARCH(1,1) models for WMT Stock} 
  \label{lb_WMT} 
\begin{tabular}{cc|cccccc} 
\\[-1.8ex]\hline 
\hline
& & \multicolumn{3}{c}{Standardized residuals} & \multicolumn{3}{c}{Squared standardized residuals} \\
& & Q(10) & Q(15) & Q(20) & Q(10) & Q(15) & Q(20) \\
\hline 
\multirow{2}{*}{ARCH(1)} & statistic & 9.0085 & 15.1256 & 20.0360 & 2.1312 & 2.4483 & 4.4991 \\
& p-value & 0.5313 & 0.4424 & 0.4557 & 0.9952 & 0.9999 & 0.9999 \\
\multirow{2}{*}{GARCH(1,1)} & statistic & 8.8064 & 14.4575 & 18.5378 & 1.6428 & 1.9398 & 4.0184 \\
& p.value & 0.5506 & 0.4912 & 0.5520 & 0.9984 & 0.9999 & 0.9999 \\
\hline
\hline 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{Results of Estimation of Two Volatility Models for WMT Stock} 
  \label{est_WMT} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline
 & ARCH(1) & GARCH(1,1) \\ 
 mu & 0.037 & 0.033 \\ 
  & (0.023) & (0.024) \\ 
 omega & 0.863$^{***}$ & 0.442$^{**}$ \\ 
  & (0.036) & (0.187) \\ 
 alpha1 & 0.192$^{***}$ & 0.140$^{***}$ \\ 
  & (0.034) & (0.040) \\ 
 beta1 &  & 0.445$^{**}$ \\ 
  &  & (0.207) \\ 
\hline \\[-1.8ex] 
Observations & 1761 & 1761 \\ 
Log Likelihood & 2506.755 & 2506.020 \\ 
Akaike Inf. Crit. & 2.850 & 2.851 \\ 
Bayesian Inf. Crit. & 2.860 & 2.863 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

>>>>

\documentclass[paper=a4, fontsize=11pt]{article} 
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{amstext}
\usepackage{subfigure}
\RequirePackage{graphicx}
\RequirePackage{longtable,multirow,hhline,tabularx,array}
\usepackage[english]{babel} 
\RequirePackage{colortbl,booktabs}
\linespread{1.5}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width = 5in]{img/cf_AMZN}
\caption{ACF and PACF of Amazon Stock}
\label{cf_AMZN}
\end{figure}

\begin{figure}[!htbp]
\centering
\includegraphics[width = 5in]{img/cf_WMT}
\caption{ACF and PACF of Walmart Stock}
\label{cf_WMT}
\end{figure}

@@

The $a_t^2$ series is then used to check for conditional heteroscedasticity (ARCH effects). To consolidate the observation results in Figure \ref{cf_AMZN}.(c), the ARCH effect exists in log return series, we perform the Ljung–Box statistics Q(m) to the $\{a_t^2\}$ series. The null hypothesis is that the first m lags of ACF of the $a_t^2$ series are zero. The results of Ljung–Box test shows an ARCH effect exists in this log return series with Q(5) = 9.6519, the p-value of which is close to zero.

Using the same method above to analyze the ACF and PACF of WMT log returns shown in Figure \ref{cf_WMT}, we conclude that the WMT log returns' mean equation is also an ARMA(0,0) process. And there exists an ARCH effect in WMT's log return series. Although someone may argues that Figure \ref{cf_WMT} shows significant correlation at lag-14 and lag-27, the EACF results in Table \ref{eacf_WMT} provides the evidence that ARMA(0,0) is proper.

\begin{table}[!htbp] \centering 
  \caption{EACF of Log Returns of Walmart Stock} 
  \label{eacf_WMT} 
\begin{tabular}{c|cccccccccccccc} 
\hline 
\hline
AR/MA & 0 &1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13\\
\hline 
0 & o & o & o & o & o & o & o & o & o & o & o & o & o & x \\ 
1 & x & o & o & o & o & o & o & o & o & o & o & o & o & o \\ 
2 & x & x & o & o & o & o & o & o & o & o & o & o & o & o \\ 
3 & x & x & x & o & o & o & o & o & o & o & o & o & o & o \\ 
4 & x & x & x & x & o & o & o & o & o & o & o & o & o & o \\ 
5 & x & x & x & x & x & o & o & o & o & o & o & o & o & o \\ 
6 & x & x & x & o & x & x & o & o & o & o & o & o & o & o \\ 
7 & x & x & o & x & x & x & x & o & o & o & o & o & o & o \\ 
\hline
\end{tabular} 
\end{table}

@@

Similar results will be derived for the log return series of Walmart stock. We entertain an ARCH(4) model and a GARCH(1,1) model as the alternative volatility equations:
\[ r_t = \mu+a_t, a_t = \sigma_t \epsilon_t \]
\[ \text{ARCH(4): } \sigma_t^2 = \alpha_0+\alpha_1 a_{t-1}^2+\alpha_2 a_{t-2}^2+\alpha_3 a_{t-3}^2+\alpha_4 a_{t-4}^2 \]
\[ \text{GARCH(1,1): } \sigma_t^2= \alpha_0+\alpha_1 a_{t-1}^2+\beta_1 \sigma_{t-1}^2 \]
where $\epsilon_t \sim N(0,1)$.

@@

\begin{table}[!htbp] \centering 
  \caption{Results of Estimation of Two Volatility Models for AMZN Stock} 
  \label{est_AMZN} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline
 & ARCH(1) & GARCH(1,1) \\ 
 $\mu$ & 0.115$^{**}$ & 0.137$^{***}$ \\ 
  & (0.046) & (0.046) \\ 
 $\alpha_0$ & 3.515$^{***}$ & 1.020$^{***}$ \\ 
  & (0.149) & (0.344) \\ 
 $\alpha_1$ & 0.168$^{***}$ & 0.129$^{***}$ \\ 
  & (0.036) & (0.032) \\ 
 $\beta_1$ &  & 0.637$^{***}$ \\ 
  &  & (0.098) \\ 
\hline \\[-1.8ex] 
Observations & 1761 & 1761 \\ 
Log Likelihood & -3724.855 & -3720.010 \\ 
Akaike Inf. Crit. & 4.234 & 4.229 \\ 
Bayesian Inf. Crit. & 4.243 & 4.242 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

\begin{table}[!htbp] \centering 
  \caption{Ljung-Box tests for ARCH(4) and GARCH(1,1) models for WMT Stock} 
  \label{lb_WMT} 
\begin{tabular}{cc|cccccc} 
\\[-1.8ex]\hline 
\hline
& & \multicolumn{3}{c}{Standardized residuals} & \multicolumn{3}{c}{Squared standardized residuals} \\
& & Q(10) & Q(15) & Q(20) & Q(10) & Q(15) & Q(20) \\
\hline 
\multirow{2}{*}{ARCH(4)} & statistic & 9.6623 & 15.0804 & 19.5692 & 1.4971 & 1.9193 & 3.6344 \\
& p-value & 0.4706 & 0.4456 & 0.4852 & 0.9989 & 0.9999 & 0.9999 \\
\multirow{2}{*}{GARCH(1,1)} & statistic & 8.8064 & 14.4575 & 18.5378 & 1.6428 & 1.9398 & 4.0184 \\
& p.value & 0.5506 & 0.4912 & 0.5520 & 0.9984 & 0.9999 & 0.9999 \\
\hline
\hline 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{Results of Estimation of Two Volatility Models for WMT Stock} 
  \label{est_WMT} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline
 & ARCH(4) & GARCH(1,1) \\ 
  $\mu$ & 0.024 & 0.033 \\ 
  & (0.023) & (0.024) \\ 
 $\alpha_0$ & 0.773$^{***}$ & 0.442$^{**}$ \\ 
  & (0.042) & (0.187) \\ 
 $\alpha_1$ & 0.130$^{***}$ & 0.140$^{***}$ \\ 
  & (0.035) & (0.040) \\ 
 $\alpha_2$ & 0.000 &  \\ 
  & (0.018) &  \\ 
 $\alpha_3$ & 0.034 &  \\ 
  & (0.024) &  \\ 
 $\alpha_4$ & 0.112$^{***}$ &  \\ 
  & (0.040) &  \\ 
 $\beta_1$ &  & 0.445$^{**}$ \\ 
  &  & (0.207) \\ 
\hline \\[-1.8ex] 
Observations & 1761 & 1761 \\ 
Log Likelihood & -2498.390 & -2506.020 \\ 
Akaike Inf. Crit. & 2.844 & 2.851 \\ 
Bayesian Inf. Crit. & 2.863 & 2.863 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

Following the same logic above and combining the results in Table \ref{lb_WMT} and Table \ref{est_WMT}, the ARCH(4) model is more adequate for volatility in log returns of Walmart stock. Thus, we propose an ARMA(0,0)+ARCH(4) model to depict the log return series of Walmart stock:
\[ r_t = 0.024+a_t\]
\[ a_t = \sigma_t \epsilon_t, \epsilon_t \sim N(0,1) \]
\[ \sigma_t^2 = 0.773+0.13a_{t-1}^2+0.034a_{t-3}^2+0.112a_{t-4}^2 \]
\newpage
